Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-03 _02_filtering_data.Rmd
no more separate raw data

```{r echo=FALSE}
# make figure of canonical data with added errors
figure_raw <-
  ggplot()+
  geom_point(data = data_copy,
            aes(x, y),
            col = "grey",
            alpha = 1,
            shape = 4,
            size = 0.2)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        plot.title = element_text(
          face = "bold",
          margin = margin(t = 30, b = -30),
          hjust = 0.1
        ))+
  coord_equal()+
  labs(colour = NULL)+
  labs(
    title = "(a)"
  )
```

@@

```{r echo=FALSE}
# plot data inside and outside bbox
fig_filter_bounds <-
  ggplot()+
  geom_point(data = data_inside_bbox,
             aes(x, y),
             col = pal[3],
             alpha = 1, size = 0.2)+
  geom_point(data = data_copy[!data_inside_bbox,
                              on = c("x", "y")],
             aes(x, y),
             col = "grey",
             shape = 4,
             size = 0.2)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  geom_hline(yintercept = c(0.5, 1),
             col = "grey",
             lty = 2)+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        plot.title = element_text(
          face = "bold",
          margin = margin(t = 30, b = -30),
          hjust = 0.1
        ))+
  theme(plot.background = element_rect(fill = NA))+
  coord_equal(expand = T)+
  labs(
    title = "(b)"
  )

# wrap plots
plot_figure <-
  wrap_plots(list(figure_raw, fig_filter_bounds))

ggsave(plot_figure, filename = "figures/fig_02_bounds.png", 
       width = 170, height = 150, units = "mm")
```

@@

```{r echo=FALSE}
# data plot
fig_outlier_remove <-
  ggplot()+
  geom_path(data = data_copy,
            aes(x, y),
            col = "grey",
            lwd = 0.2)+
  geom_point(data = data_copy[500:800, ],
             aes(x, y),
             # size = 0.5,
             shape = 4, col = pal[4])+
  geom_point(data = data_copy[!data_copy[500:800, ],
                              on = c("x", "y")],
             aes(x, y, 
                 col = (in_speed >= 0.03 & out_speed >= 0.03),
                 shape = (in_speed >= 0.03 & out_speed >= 0.03),
                 size = (in_speed >= 0.03 & out_speed >= 0.03)),
             show.legend = F,
             alpha = 1)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  scale_color_manual(values = c(pal[3], pal[1]))+
  scale_shape_manual(values = c(1, 4))+
  scale_size_manual(
    values = c(0.5, 2)
  )+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_equal()+
  theme(plot.background = element_rect(fill = NA))
```

@@

```{r echo=FALSE}
# save figure
ggsave(fig_outlier_remove, 
       filename = "figures/fig_03_filter_speed.png", 
       width = 80, height = 150, units = "mm")
```

>>>>

```{r echo=FALSE}
# make figure of canonical data with added errors
# figure_raw <-
#   ggplot()+
#   geom_point(data = data_copy,
#             aes(x, y),
#             col = "grey",
#             alpha = 1,
#             shape = 4,
#             size = 0.2)+
#   geom_path(data = data,
#             aes(x, y),
#             col = "grey20",
#             alpha = 1)+
#   ggthemes::theme_few()+
#   theme(axis.text = element_blank(),
#         axis.title = element_blank(),
#         plot.title = element_text(
#           face = "bold",
#           margin = margin(t = 30, b = -30),
#           hjust = 0.1
#         ))+
#   coord_equal()+
#   labs(colour = NULL)+
#   labs(
#     title = "(a)"
#   )
```

@@

```{r echo=FALSE}
# plot data inside and outside bbox
fig_filter_bounds <-
  ggplot()+
  geom_point(data = data_inside_bbox,
             aes(x, y),
             col = pal[3],
             alpha = 1, size = 0.2)+
  geom_point(data = data_copy[!data_inside_bbox,
                              on = c("x", "y")],
             aes(x, y),
             col = "grey",
             shape = 4,
             size = 0.2)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  geom_hline(yintercept = c(0.5, 1),
             col = "grey",
             lty = 2)+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        plot.title = element_text(
          face = "bold",
          margin = margin(t = 30, b = -30),
          hjust = 0.1
        ))+
  theme(plot.background = element_rect(fill = NA))+
  coord_equal(expand = T)+
  labs(
    title = "(a)"
  )
```

@@

```{r echo=FALSE}
# data plot
fig_outlier_remove <-
  ggplot()+
  geom_path(data = data_copy,
            aes(x, y),
            col = "grey",
            lwd = 0.2)+
  geom_point(data = data_copy[500:800, ],
             aes(x, y),
             size = 0.5,
             alpha = 0.6,
             shape = 4, col = pal[4])+
  geom_point(data = data_copy[!data_copy[500:800, ],
                              on = c("x", "y")],
             aes(x, y, 
                 col = (in_speed >= 0.03 & out_speed >= 0.03),
                 shape = (in_speed >= 0.03 & out_speed >= 0.03),
                 size = (in_speed >= 0.03 & out_speed >= 0.03)),
             show.legend = F,
             alpha = 1)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  scale_color_manual(values = c(pal[3], pal[1]))+
  scale_shape_manual(values = c(1, 4))+
  scale_size_manual(
    values = c(0.2, 2)
  )+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        plot.title = element_text(
          face = "bold",
          margin = margin(t = 30, b = -30),
          hjust = 0.1
        ))+
  coord_equal()+
  theme(plot.background = element_rect(fill = NA))+
  labs(
    title = "(b)"
  )
```

@@

```{r echo=FALSE}
# wrap plot
figure_01 =
  wrap_plots(
    fig_filter_bounds,
    fig_outlier_remove
  )

# save figure
ggsave(figure_01, 
       filename = "figures/fig_02_filtering_data.png", 
       width = 170, height = 150, units = "mm")
```
